### 2016-06-28 Docs/makefiles/makefiles.tex
a bit more docs on TEST and FSANITIZER

>>>>

\section{Special Debugging Executables}

\boxlib\ has several options that produce executables that can help
track down memory issues, uninitialized variables, NaNs, etc.

\begin{itemize}

\item {\tt NDEBUG}

  \otherindex{{\tt GNUmakefile}}{NDEBUG} To generate an executable
  with debugging information included in the executable (e.g., to be
  interpreted by the debugger, {\tt gdb}), compile with {\tt NDEBUG
    :=\ }.  This will usually add {\tt -g} to the compile line and
  also lower the optimization.  For {\tt gfortran} it will add several
  options to catch uninitialize variables, bounds errors, etc.

\item {\tt TEST}

  Setting {\tt TEST := t}\otherindex{{\tt GNUmakefile}}{TEST=t} will
  enable routines in \boxlib\ that intercept floating point
  exceptions, including NaNs, divide by zero, and overflow.  When one
  of these is hit, the code will abort, and the backtrace information
  will be output to a file {\tt Backtrace.N}, where {\tt N} is the
  processor number.  BoxLib will also initialize \multifab s with
  signaliing NaNs to help uncover any floating point issues.

  This is also useful to diagnose deadlocks in parallel regions.
  If the code is hanging, doing ``control-C'' will be intercepted
  and the code will generate a backtrace which will identify
  where in the code there was a deadlock.

  Behind the scenes, \boxlib\ implements this capability via the
  Linux/Unix {\tt feenableexcept} function (this is in {\tt
    backtrace\_c.cpp} in \boxlib).

\item {\tt FSANITIZER}

  For {\tt gfortran}, {\tt gcc}, {\tt g++}, setting {\tt FSANITIZER :=
    t}\otherindex{{\tt GNUmakefile}}{FSANITIZER} will enable the
  address sanitizer support built into GCC.  This is enabled through
  integration with \url{https://github.com/google/sanitizers} in GCC.
